---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# impfpp - tidy WEO forecast data 

<!-- badges: start -->
<!-- badges: end -->

Small package to download and tidy forecast data from the IMF World Economic Outlook.

## Installation

You can install the development version of imfpp from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("fredbec/imfpp")
```

## Example

If you simply want to download, tidy and save all available forecasts for GDP growth and inflation (and include info on country groups), run the following
```{r example, eval = FALSE}
library(imfpp)
## basic example code
download.process.weo()
```

If you want different variables, exclude country groups and/or don't want explicit missing values, alternatively run

```{r alts, eval = FALSE}
download.process.weo(sheets = c("ngdp_rpch", "bca_gdp_bp6"))
download.process.weo(explicitMissings = FALSE)
download.process.weo(includeCountryGroups = FALSE)
```

The variables included in the dataset are as follows:

| Variable      | Explanation           |
| ------------- |:------------- |
| country       | country names as they appear in the WEO data (with minimal changes) |
| WEO_Country_Code      | country codes as they appear in the WEO data     |
| ISOAlpha_3Code | another country code     |
| target        | target variable, one of ngdp_rpch (GDP growth), pcpi_pch (CPI inflation), bca_gdp_bp6 (account balance, percent of GDP) |
| target_date | the year the forecast is made for |
| forecast_season | the season the forecast was made in (S for Spring, F for fall) |
| horizon | the forecast horizon (e.g. 0.5 refers to a forecast from spring made for the current year, 1 refers to a forecast from fall made for next year) |
| forecast_year | the year the forecast was made (forecast_year + horizon = target_date) |
| type | prediction or data correction (-> "historical") |
| prediction | predicted value for the target |
| cgroup | is country a country group (e.g. "Advanced Economies")|
| economy | categorization of country economy (Adv. Economies, Emerging Market Economies, Low-Income Developing Countries) |
| euro | categorization into Euro Area countries (binary) |
| g7 | categoriation into G7 countries (binary) |
| g20 | categorization into G20 countries (binary) |
| geoEmer | categorization of Emerging Market and Middle-Income Economies into geographical regions (Asia, Europe, Latin America, Middle East North Africa and Pakistan, Africa) |
| geolInc | categorization of Low-Income Developing Economies into geographical regions (Asia, Latin America, Sub-Saharan Africa, Others) |
| oil | categorization of Oil-Producing countries |


ToDo: Embed plots for available data.

```{r plot} 
library(ggplot2)
library(RColorBrewer)
```

